### 2016-04-26 doc/publications/plos16/plos16.tex
small changes

\section*{Notes}
\begin{itemize}
\item what are you guys editing this with?  what about some carrige
  returns or line feeds or something!
\item Are we going to use the TCGA data in this paper?
\item are we going to run sparkML or Curesed forest on the extended
  simulation data \cite[]{Genuer.et.al.2010}? Has Aidan done this already?
\end{itemize}

@@

I will use the R terms from the package RandomForests whcih incoporates the original Fortran code by Brieman and
Cutler. We consider the parameters:
\begin{itemize}
\item \texttt{max_depth} the size (complexity) of the individual trees
\item \texttt{ntree} the number of trees 
\item \texttt{mtry} --  the number of variables considered at each split (if \texttt{mtry}=$p$, we have a boosted decison
  tree model \marginpar{is this right?}
\end{itemize}

>>>>

\section*{Notes}
\begin{itemize}
\item what are you guys editing this with?  what about some carriage
  returns or line feeds or something!
\item Are we going to use the TCGA data in this paper?
\item are we going to run sparkML or Cursed forest on the extended
  simulation data \cite[]{Genuer.et.al.2010}? Has Aidan done this already?
\end{itemize}

@@

I will use the R terms from the package RandomForests whcih incoporates the original Fortran code by Brieman and
Cutler. We consider the parameters:
\begin{itemize}
\item the size and complexity of the individual trees is controlled in RandomForests by setting \texttt{nodesize}, the
  minimum size of terminal nodes. It is controlled in Spark.ML by setting \texttt{maxDepth}, the maximum depth of each
  tree in the forest. The SparkML documentation somewhat unhelpfully sets \texttt{maxDepth=4} in their classification
  example\footnote{the documentation is available at \url{http://spark.apache.org/docs/latest/mllib-ensembles.html} }.
  In the ATCG example the RF code produced trees with depths of 30+. We note that Random forests are a way of averaging
  multiple deep decision trees, trained on different parts of the same training set, with the goal of reducing the
  variance. \url{https://en.wikipedia.org/wiki/Random_forest} and refs therein.  
\marginpar{are we including this  example?  Supplementary info?}
\item \texttt{ntree} the number of trees 
\item \texttt{mtry} --  the number of variables considered at each split (if \texttt{mtry}=$p$, we have a boosted decison
  tree model \marginpar{is this right?}
\end{itemize}
